Thesis Title

### 2022-04-07 chapters/introduction.tex
add introduction to chap 4

Traditional approaches to laboratory diagnosis of viral infections have been (1) direct detection in patient material of virions, viral antigens, or viral nucleic acids, (2) isolation of the virus in cultured cells, followed by identification of the isolate, and (3) detection and measurement of antibodies in patient serum (serology) \citep{burrell_laboratory_2017}. 
Viral diagnostics is therefore generally organised into two primary categories, indirect and direct detection, depending on the method used.

>>>>

Traditional approaches to laboratory diagnosis of viral infections have been (1) direct detection in patient material of virions, viral antigens, or viral nucleic acids, (2) isolation of the virus in cultured cells, followed by identification of the isolate, and (3) detection and measurement of antibodies in patient serum (serology) \citep{burrell_laboratory_2017}. 
Viral diagnostics is therefore generally organised into two primary categories, indirect and direct detection, depending on the method used \ref{fig:figure_viral}.

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{figures/introduction/viral.pdf}
\caption{\textbf{Principles of current processing of viral pathogens.} Schematic representation of the current workflow for processing samples for viral pathogens is presented. Samples that are likely to be normally sterile are often cultured and isolated in suitable host cell lines (indirect identification). This supports the identification through microscopy of molecular methods, but the virus can take weeks to propagate. Direct identification is much faster, relying on nucleic acid detection of immunologic assays for the identification of the pathogen, without the need of virus propagation.}
\label{fig:figure_viral}
\end{figure*}
